Randomforest

### 2019-05-13 partialrda.Rmd
1->100

```{r anova species}
anova.species <- permutest(rda.species, method="reduced", perm=1)
anova.species %>% anotab %>% kable
```

@@

```{r anova genus}
anova.genus <- permutest(rda.genus, method="reduced", perm=1)
anova.genus %>% anotab %>% kable
```

```{r anova genus core}
anova.genus.core <- permutest(rda.genus.core, method="reduced", perm=1)
anova.genus.core %>% anotab %>% kable
```

>>>>

```{r anova species}
anova.species <- permutest(rda.species, method="reduced", perm=100)
anova.species %>% anotab %>% kable
```

@@

```{r anova genus}
anova.genus <- permutest(rda.genus, method="reduced", perm=100)
anova.genus %>% anotab %>% kable
```

```{r anova genus core}
anova.genus.core <- permutest(rda.genus.core, method="reduced", perm=100)
anova.genus.core %>% anotab %>% kable
```
